---
title: "Notebook"
output: rmarkdown::github_document
---

```{r}
library('readxl')
library("dplyr")
library("ggpubr")
library('caret')
```
Reading Data from csv File
Removing the Unwanted Categorical Features from Dataset

```{r}

data_original <- read.csv("/home/harsh/Desktop/Regression_Analysis/Regression_Project/data.csv")
data_original

cols.dont.want <- c("X","ID","Name", "Photo", "Nationality", "Flag", "Potential", "Club", "Club.Logo", "Preferred.Foot", "Work.Rate", "Body.Type", "Real.Face", "Position", "Jersey.Number", "Joined", "Loaned.From", "Contract.Valid.Until" ) 
data <- data_original[, ! names(data_original) %in% cols.dont.want, drop = F]
data
```

Converting all Values to numeric type,
Removing all '€', 'M', 'K','ft inches', 'lbs', 'error ranges' from data
Replacing All NA/Missing Values with Mean of that column

```{r}
data$Value <- gsub("€", "", data$Value)
data$Value <- as.numeric(gsub("M", "000", data$Value))
data$Release.Clause <- gsub("€", "", data$Release.Clause)
data$Release.Clause <- as.numeric(gsub("M", "000", data$Release.Clause))
data$Wage <- gsub("€", "", data$Wage)
data$Wage <- as.numeric(gsub("K", "", data$Wage))
data$Height <- as.numeric(gsub("\'", ".", data$Height))
data$Weight <- as.numeric(gsub("lbs", "", data$Weight))

for (i in c(11:38))
  data[,i]<- as.numeric(gsub("+", ".", data[,i],fixed=TRUE))
data

for(i in 1:ncol(data))
  data[is.na(data[,i]), i] <- mean(data[,i], na.rm = TRUE)
data
```
Normalizing the columns of the dataset to range [0,1] so that all features get equal weightage in model.
Normalizing to (0,1] instead of standardizing to [-1,1] because BoxCox transformation requires y to be strictly positive.

```{r}
#Uncomment to standardize to [-1,1]
#data_scaled <- as.data.frame(scale(data))
#data_scaled

# calculate the pre-process parameters from the dataset
preprocessParams <- preProcess(data, method=c("range"))
# summarize transform parameters
print(preprocessParams)
# transform the dataset using the parameters
data_scaled <- predict(preprocessParams, data) + c(0.0000001)
# summarize the transformed dataset
for(i in 1:ncol(data))
  data_scaled[is.na(data_scaled[,i]), i] <- mean(data_scaled[,i], na.rm = TRUE)
  data_scaled[is.infinite(data_scaled[,i]), i] <- mean(data_scaled[,i], na.rm = TRUE)
#data_scaled
summary(data_scaled)
```

Shuffle Rows of DataSet
Seperate the train set and test set as 70% and 30% of given dataset

```{r}
data_shuffled <- data_scaled[sample(nrow(data_scaled)),]
r1 <- as.integer(nrow(data_shuffled)*0.7) #row number at which splitting takes place
data_train <- data_shuffled[1:r1,]
data_test <- data_shuffled[(r1+1):nrow(data_shuffled),]

data_shuffled
data_train
data_test
```

Sepatating the Dependent and Independent Variables from Training Data
Creating Variables x_train, y_train, x_test, y_test

```{r}
not_training_features <- c("Overall") 
x_train <- as.matrix(data_train[, ! names(data_train) %in% not_training_features, drop = F])
y_train <- as.matrix(data_train[,"Overall", drop = F])
x_test <- as.matrix(data_test[, ! names(data_test) %in% not_training_features, drop = F])
y_test <- as.matrix(data_test[,"Overall", drop = F])

print("Dimensions :")
print("x_train : ")
print(dim(x_train))
print("x_test : ")
print(dim(x_test))
print("y_train : ")
print(dim(y_train))
print("y_test : ")
print(dim(y_test))
```

Fitting basic Multiple Linear Regression Model 

```{r}
lin_model1<-Overall~Age+Value+Wage+Special+International.Reputation+Weak.Foot+Skill.Moves+Height+Weight+LS+ST+RS+LW+LF+CF+RF+RW+LAM+CAM+RAM+LM+LCM+CM+RCM+RM+LWB+LDM+CDM+RDM+RWB+LB+LCB+CB+RCB+RB+Crossing+Finishing+HeadingAccuracy+ShortPassing+Volleys+Dribbling+Curve+FKAccuracy+LongPassing+BallControl+Acceleration+SprintSpeed+Agility+Reactions+Balance+ShotPower+Jumping+Stamina+Strength+LongShots+Aggression+Interceptions+Positioning+Vision+Penalties+Composure+Marking+StandingTackle+SlidingTackle+GKDiving+GKHandling+GKKicking+GKPositioning+GKReflexes+Release.Clause

fit1<-lm(lin_model1,data_train)
fit1
summary(fit1)
print("Number of Parameters Learnt = ")
print(length(fit1$coefficients))
```

In the above linear model, we see - 

1. 16 Coefficients could not be obtained due to singularity of (X.T X) due to multicollinearity of regressors.
2. As p-value of Global Hypothesis is < 0.05, we reject the Null hypothesis of Global Hypothesis test. Atleast some regressors are significant.
3. As global null hypothesis is rejected, we see individual significance test for regressors. The regressors which have p-value < 0.05 are significant, we will include those in our model. As Global hypothesis does not test intercept, we include Intercept irrespective of p-value.

```{r}
#storing True/False for Inclusion/Exclusion of all regressors based on p-value < 0.05
toselect.x <- summary(fit1)$coeff[-1,4] < 0.05
#toselect.x
#storing names of regressors that have p-value < 0.05
relevant.x <- names(toselect.x)[toselect.x == TRUE] 
#relevant.x
#linear model formula with only significant variables
sig.formula <- as.formula(paste("Overall ~",paste(relevant.x, collapse= "+")))
print("New Formula ")
print(sig.formula)
lin_model2 <- sig.formula
fit2<-lm(lin_model2,data_train)
fit2
summary(fit2)

print("Number of Parameters Learnt = ")
print(length(fit2$coefficients))
```

See that -
1. Reduced number of parameters learnt (= p+1) for (b0, b1, b2, ... , bp) to 39 from initial value of 71
2. Insignificant decrease in R^2 as compared to reduction in number of parameters - 
      R^2 has decreased from 0.878 to 0.8775 
      Adjusted R^2 has decreased from 0.8775 to 0.8772
      

Graphical Analysis of Residuals - 

Plotting Residuals vs Y (e_i vs y_i), and QQ plot to see if Variance is stabilized

```{r}
plot(fit2)
```

Observations - 

1. Residuals vs Fitted :
    Most Residuals are equally spread along the horizontal line, but  change as the Fitted Values are very high. (Outliers)
2. Normal QQ Plot :
    Data is normally distributed except few outliers.
3. Scale Location Plot: 
    Data is evenly spread except for outliers when fitted values are very high
4. Residuals vs Leverage :
    Cook's Distance Lines are not seen in plot, this means all cases are well inside Cook's distance lines. There are no outliers that alone are extremely influential to the regression results. 


Density Plot of Residuals looks like it has a Normal Distribution :
```{r}
plot(density(resid(fit2)))
```

Applying Shapiro-Wilk's Normalcy Test :
  H_0 : Sample is Normal, H_a: Sample not normal
  
```{r}
shapiro.test(resid(fit2)[1:5000])
shapiro.test(resid(fit2)[5001:10000])
shapiro.test(resid(fit2)[10001:length(resid(fit2))])
```

As p-value is < 0.05 for our data, Shapiro-Wilk test says that Residuals are not normally distributed.
But Shapiro-Wilk test should be applied only for n<50, as it generally always rejects Large Datasets, even if they lie close to Normal Distribution. 

We simulate Normal Distribution with Slight Deviation, and show that Shapiro-Wilk Test rejects 50% of all n=5000 size datasets.
```{r}
x <- replicate(1000, { # generates 100 different tests on each distribution
                     c(shapiro.test(rnorm(1000)+c(0,0,1,0,0))$p.value, #$
                       shapiro.test(rnorm(5000)+c(0,0,1,0,0))$p.value) #$
                    } # rnorm gives a random draw from the normal distribution
               )
rownames(x) <- c("n1000","n5000")
rowMeans(x<0.05)
```
For large datasets, Normalcy Tests are not significant because of Central Limit Theorem.


We use Box-Cox Transformation to stabilize Variance.

```{r}
model3_formula <- as.formula(paste("data_train$Overall ~",paste("data_train$",paste(relevant.x, collapse= "+data_train$"))))
lambda<-boxCox(model3_formula,objective.name="Log-Likelihood",plotit = TRUE)
ind<-which(lambda$y == max(lambda$y))
lambda.max<-lambda$x[ind]
Overall.tr<-bcPower(data_train$Overall,lambda = lambda.max)
model3_formula <- as.formula(paste("Overall.tr ~",paste(relevant.x, collapse= "+")))
model3 <-model3_formula
fit3<-lm(model3,data_train)
summary(fit3)
```

See that the values of R^2 and Adjusted R^2 have increased. 
      R^2 has decreased from 0.8775 to 0.8815
      Adjusted R^2 has decreased from 0.8772 to 0.8811










